---
title: "R Markdown Debugging Demo"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
f <- function(x) {
  if (x < 0) {
    stop("x should not be < 0")
  } else {
    return(2 * x)
  }
}

g <- function(x) {
  if (x < 0) {
    browser()
  } else {
    return(2 * x)
  }
}
```

### This works
```{r}
f(1)
```

### Interactive debugging

When rendering the document with `rmarkdown::render()`, the render process will stop at the `browser()` statement as defined in function `g()`. By default, output gets captured by RMarkdown, so no output is shown on the console. To enable debugging as usual, call `sink()`.

To execute the blocks below, replace `{}` with `{r}`:

```{}
g(-1)
```

### Interactive debugging with call stack

Setting the error function to a function that calls `sink()`, prints out the call stack and invokes `recover()` can be a powerful combination to immediately get information on the location of the error and interactively inspect the issue. See https://rlang.r-lib.org/reference/trace_back.html for details.

```{r}
options(error = function() {
  sink()
  print(rlang::trace_back(bottom = sys.frame(-1)))
  recover()
})

f(-1)
```